Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2021-11-01 prevalence_testing/postshocktest2021draft.tex
addition with corollary

% function definition
\newcommand{\R}{\mathbb{R}}
\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\dbf}{\textbf{d}}
\newcommand{\y}{\textbf{y}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Y}{\textbf{Y}}
\newcommand{\L}{\textbf{L}}
\newcommand{\Hist}{\mathcal{H}}
\newcommand{\Prob}{\mathbb{P}}
\def\mbf#1{\mathbf{#1}} % bold but not italic
\def\ind#1{\mathrm{1}(#1)} % indicator function
\newcommand{\simiid}{\stackrel{iid}{\sim}} %[] IID 
\def\where{\text{ where }} % where
\newcommand{\indep}{\perp \!\!\! \perp } % independent symbols
\def\cov#1#2{\mathrm{Cov}(#1, #2)} % covariance 
\def\mrm#1{\mathrm{#1}} % remove math
\newcommand{\reals}{\mathbb{R}} % Real number symbol
\def\t#1{\tilde{#1}} % tilde
\def\normal#1#2{\mathcal{N}(#1,#2)} % normal
\def\mbi#1{\boldsymbol{#1}} % Bold and italic (math bold italic)
\def\v#1{\mbi{#1}} % Vector notation
\def\mc#1{\mathcal{#1}} % mathical
\DeclareMathOperator*{\argmax}{arg\,max} % arg max
\DeclareMathOperator*{\argmin}{arg\,min} % arg min
\def\E{\mathbb{E}} % Expectation symbol
\def\mc#1{\mathcal{#1}}
\def\var#1{\mathrm{Var}(#1)} % Variance symbol
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} % checkmark
\newcommand\red[1]{{\color{red}#1}}
\def\bs#1{\boldsymbol{#1}}
\def\P{\mathbb{P}}

\newcommand{\ceil}[1]{\lceil #1 \rceil}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert} % A norm with 1 argument
\DeclareMathOperator{\Var}{Var} % Variance symbol

@@

Suppose $p_1, \ldots, p_{n+1}$ be a sequence of pairwise independent $p$-values  with $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$, where $\alpha$ is the significance level, $\kappa$ is a real-valued constant in $[0,1]$, and  $p_1$ is the p-value of the time series of interest. If $\P(p_1 \leq \alpha) \neq 0.5$,
\begin{align*}
  \E \bigg\{\left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
  - I( p_1 \leq  \alpha) \right|\bigg\}
  \to  \begin{cases}
    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
  \end{cases}
\end{align*}
%That is, as $n\to \infty$, the expected misclassification rate of voting converges to 
%\begin{align*}
%  \begin{cases}
%    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
%    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
%  \end{cases}
%\end{align*}
%and the limiting misclassification rate is bounded by 0.5.
\end{prop}

@@

@@

\vspace*{0.5cm}\noindent\textbf{This needs some work (ignore for now)} Now consider a case where there exists a $2 \leq i' < n + 1$ where $\x_{1,t} = \x_{i',t}$. Now suppose for simplicity that $T^*_{j'} = T^*_1$ and that $T_{i'} = T_1$ where $T_1 > T^*_1 + q_1 + q_2 + 2$. This assumes that we have data for the first time series beyond the shock point. We will show that when there is a covariate clone of the time series under study, then estimation in this series will approximate estimation in the time series under study provided that the underlying variability is very small relative to the signal. To see this, consider $t > T^*_1$, where 
\begin{align*}
y_{1,t} &= \eta_1 + \mu_\alpha + \delta_1'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} + \sum_{j=0}^{q_2-1}(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{1} + \varepsilon_{1,t}, \\
y_{i',t} &= \eta_{i'} + \mu_\alpha + \delta_{i'}'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} + \sum_{j=0}^{q_2-1}(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{i'} + \varepsilon_{i',t}, \\
\hat y_{1,t} &= \hat \eta_1 + \hat{\alpha}_1(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat y_{1,t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}, \\
\hat y_{i',t} &= \hat\eta_{i'} + \hat{\alpha}_{i'}(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat y_{i',t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}, 
\end{align*}
where $\alpha_j(\x) = \mu_\alpha + \delta_j'\x$, and we have 
\begin{align*}
  |y_{1,t} - \hat y_{1,t}| &= \Bigg\vert (\eta_1 - \hat\eta_1) + (\alpha_1 - \hat{\alpha}_1(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} - (\hat\phi_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat{y}_{1,t-j}\left] \\ 
  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} - (\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{1,t} \Bigg\vert \\
  |y_{i',t} - \hat y_{i',t}| &= \Bigg\vert (\eta_{i'} - \hat\eta_{i'}) + (\alpha_{i'} - \hat{\alpha}_{i'}(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} - (\hat\phi_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat{y}_{i',t-j}\left] \\ 
  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} - (\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{i',t} \Bigg\vert.
\end{align*}
\textbf{Needs finishing, but the argument is simple: estimation uncertainty declines as error variance decreases. And differences in the random effects decrease as variability decreases.} \vspace*{0.5cm}

\vspace*{0.5cm} We now demonstrate an idealized setting in which the above logic holds. We first present some intermediary technical results and definitions. Let $\lambda_{\text{max},\theta_k}$, $\lambda_{\text{max},\theta_\delta}$, $\lambda_{\text{max},\gamma}$ respectively be the largest eigenvalues of $\Sigma_{\theta_k}$, $\Sigma_{\delta}$, and $\Sigma_{\gamma}$ for $k = 1,\ldots,q_2$. Define  
\begin{align*}
  \mu_{\min} &= \min\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\min(\mu_\delta),\min(\mu_{\theta_k}),\min(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \mu_{\max} &= \max\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\max(\mu_\delta),\max(\mu_{\theta_k}),\max(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \lambda_{\max} &= \max\left(\lambda_{\text{max},\theta_k}, \lambda_{\text{max},\theta_\delta}, \lambda_{\text{max},\gamma}; k = 1,\ldots,q_2\right), \\
  \sigma^2_\max &= \max\left(\sigma^2_\eta,\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_\alpha,\sigma^2_{\tilde\phi_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right).  
\end{align*}

>>>>

% function definition
\newcommand{\R}{\mathbb{R}}
\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\dbf}{\textbf{d}}
\newcommand{\y}{\textbf{y}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Y}{\textbf{Y}}
\newcommand{\L}{\textbf{L}}
\newcommand{\Hist}{\mathcal{H}}
\newcommand{\Prob}{\mathbb{P}}
\def\mbf#1{\mathbf{#1}} % bold but not italic
\def\ind#1{\mathrm{1}(#1)} % indicator function
\newcommand{\simiid}{\stackrel{iid}{\sim}} %[] IID 
\def\where{\text{ where }} % where
\newcommand{\indep}{\perp \!\!\! \perp } % independent symbols
\def\cov#1#2{\mathrm{Cov}(#1, #2)} % covariance 
\def\mrm#1{\mathrm{#1}} % remove math
\newcommand{\reals}{\mathbb{R}} % Real number symbol
\def\t#1{\tilde{#1}} % tilde
\def\normal#1#2{\mathcal{N}(#1,#2)} % normal
\def\mbi#1{\boldsymbol{#1}} % Bold and italic (math bold italic)
\def\v#1{\mbi{#1}} % Vector notation
\def\mc#1{\mathcal{#1}} % mathical
\DeclareMathOperator*{\argmax}{arg\,max} % arg max
\DeclareMathOperator*{\argmin}{arg\,min} % arg min
\def\E{\mathbb{E}} % Expectation symbol
\def\mc#1{\mathcal{#1}}
\def\var#1{\mathrm{Var}(#1)} % Variance symbol
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} % checkmark
\newcommand\red[1]{{\color{red}#1}}
\def\bs#1{\boldsymbol{#1}}
\def\P{\mathbb{P}}
\def\var{\mathbf{Var}}
\def\naturals{\mathbb{N}}
\def\cp{\overset{p}{\to}}
\def\clt{\overset{\mathcal{L}^2}{\to}}

\newtheorem{corollary}{Corollary}
\newcommand{\ceil}[1]{\lceil #1 \rceil}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert} % A norm with 1 argument
\DeclareMathOperator{\Var}{Var} % Variance symbol

@@

\label{votprop}Suppose $p_2, \ldots, p_{n+1}$ is  a sequence of pairwise independent $p$-values  with $\P(p_i \leq \alpha)=\kappa$ for $i = 1, \ldots, n+1$, where $\alpha$ is the significance level, $\kappa$ is a real-valued constant in $[0,1]$, and  $p_1$ is the p-value of the time series of interest. If $\P(p_1 \leq \alpha) \neq 0.5$,
\begin{align*}
  \E \bigg\{\left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
  - I( p_1 \leq  \alpha) \right|\bigg\}
  \to  \begin{cases}
    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
  \end{cases}
\end{align*}
\end{prop}

@@

\begin{lem}
  \label{gwlln}  For each $n\in \naturals$, let $c_{n1}, \ldots, c_{nn}$ be real numbers bounded by some $K > 0$, and let $X_{n1}, \ldots, X_{nn}$ be pairwise independent random variables defined on a probability space $(\Omega_n, \mc{F}_n, \P_n)$, and let $\E_n$ and $\var_n$ denote the corresponding expectation and variance. If $(b_n)$ is a sequence of positive numbers such that $b_n \uparrow \infty$ such that
    \begin{align*}
      \sum_{i=1}^n \P_n (|X_{ni}| > b_n) \to 0
      \quad \text{ and } 
      \quad \frac{1}{(b_n)^2} \sum_{i=1}^n \E_n[X_{ni}^2; |X_{ni}|\leq b_n] \to 0,
    \end{align*}
    then
    \begin{align*}
      \frac{1}{b_n} \sum_{i=1}^n c_{ni} (X_{ni} - \E_n[X_{ni}; X_{ni} \leq b_n]) \cp 0.
    \end{align*}
\end{lem}

\begin{proof}
  For each $n\in \naturals$ set
    \begin{align*}
      S_n = \sum_{i=1}^n c_{ni} X_{ni}, \quad T_n = \sum_{i=1}^n c_{ni} Y_{ni},
      \quad Y_{ni} = X_{ni} I(|X_{ni}|\leq b_n), \quad i = 1, \ldots, n.
    \end{align*}
   The goal is to show that  $(S_n- \E_n[T_n])/b_n \cp 0$. For this, it suffices to show that (1) $(T_n - S_n)/b_n \cp 0$ and (2) $(T_n - \E_n[T_n])/b_n \cp 0$ because
    \begin{align*}
      (T_n - \E_n[T_n])/b_n -(T_n - S_n)/b_n = (S_n- \E_n[T_n])/b_n .
    \end{align*}
     We first prove (1). Notice that for every $\varepsilon > 0$ and $n\in \naturals$,
    \begin{align*}
      \{|S_n- T_n| > \varepsilon\}\subseteq \bigcup_{i=1}^n \{X_{ni}\neq Y_{ni}\}
      = \bigcup_{i=1}^n \{|X_{ni}|>b_n\},
    \end{align*}
    and, as a result, by Boole's inequality we have
    \begin{align*}
      \P_n (|S_n - T_n|>\varepsilon) \leq \sum_{i=1}^n \P_n(|X_{ni}|>b_n) \to 0,
    \end{align*}
    which proves (1). Next, we prove (2). Since $\mc{L}^2$ implies convergence in probability, it suffices to show that $(T_n-\E[T_n])/b_n \clt 0$, i.e., $\var[T_n]/(b_n)^2 \to 0$. Since $X_{n1}, \ldots, X_{nn}$ are pairwise independent, so are $Y_{n1}, \ldots, Y_{nn}$, and consequently
    \begin{align*}
      \Var_n[T_n]=\sum_{i=1}^n \Var_n[Y_{ni}] \leq \sum_{i=1}^n \E_n[(c_{ni}X_{ni})^2; |X_{ni}|\leq b_n] \leq K^2\sum_{i=1}^n \E_n[(X_{ni})^2; |X_{ni}|\leq b_n].
    \end{align*}
    As a result,
    \begin{align*}
    0\leq   \frac{\Var_n[T_n]}{b_n^2}\leq K^2 \cdot  \frac{1}{b_n^2}\sum_{i=1}^n \E_n[(X_{ni})^2; |X_{ni}|\leq b_n] \to 0,
    \end{align*}
    which proves the result by sandwich theorem.
\end{proof}

\newpage
\begin{corollary}
\label{coro1}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
\begin{align*}
  \mc{I}_n = \{i = \in 2,\ldots, n+1\colon 0< w_i < 1\}.
\end{align*}
Suppose that  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$ as $n \to \infty$, and $w_i b_n\leq K$ for $i\in \mc{I}_n$ and some $K>0$, where $b_n \geq 1$ and $b_n \to \infty$ as $n\to \infty$. Assume for $i \in \mc{I}_n$,  $p_i$ are pairwise independent $p$-values  with 
\begin{align*}
  \sum_{i\in \mc{I}_n}\P(p_i \leq \alpha) = \sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_{1},
\end{align*}
where $\kappa_i =  \P(p_i \leq \alpha)\in [0,1]$ for $i \in \mc{I}_n$, $\alpha$ is the significance level, $\kappa_1 = \P(p_1 \leq \alpha)$, and  $p_1$ is the p-value of the time series of interest. If $\P(p_1 \leq \alpha) \neq 0.5$,
\begin{align*}
  \E \bigg\{\left|I\left\{ \sum_{i\in \mc{I}_n} w_i I(p_i \leq  \alpha) \geq 0.5\right\}
  - I( p_1 \leq  \alpha) \right|\bigg\}
  \to  \begin{cases}
    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
  \end{cases}
\end{align*}
\end{corollary}

\begin{proof}
  The proof is rather similar to Proposition \ref{votprop}. It suffices to show that
  \begin{align*}
   \sum_{i\in \mc{I}_n} w_i I(p_i \leq  \alpha) \cp \kappa_1 =  \P(p_1 \leq \alpha).
  \end{align*}
  and the remaining proof is the same as that of Proposition \ref{votprop} in terms of applying Dominated Convergence Theorem in the version of  convergence in probability. As $p_i$ are pairwise independent for $i\in \mc{I}_n$, $I(p_i\leq \alpha)$ are pairwise independent for $i \in \mc{I}_n$. The idea is to prove the required condition of Lemma \ref{gwlln} holds. As  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$, $b_n > 1$, and  $b_n \to \infty$ as $n \to \infty$, 
  \begin{align*}
    & \sum_{i\in \mc{I}_n} \P\big( I(p_i \leq  \alpha) > b_n\big) \to 0\\
   & \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} \E\big[ I(p_i \leq  \alpha) \,|\, I(p_i \leq  \alpha) \leq b_n\big]
     =  \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} \P\big(p_i \leq\alpha \big)
     = \frac{1}{b_n^2} \sum_{i\in \mc{I}_n} w_i \kappa_i  \to 0
  \end{align*}
  because $ \sum_{i\in \mc{I}_n} w_i \kappa_i = O(1)$ by the assumption $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_{1}$. Let $c_{ni} = w_i b_n$ for $i \in \mc{I}_n$. Since $w_i b_n\leq K$ for some $K > 0$ and $b_n$, we have 
  \begin{align*}
    & \frac{1}{b_n} \sum_{i\in \mc{I}_n}  c_{ni} \big(  I(p_i \leq  \alpha) - \P( I(p_i \leq  \alpha) \, |\,  I(p_i \leq  \alpha)  \leq b_n )  \big) \\
  = \quad     &\frac{1}{b_n} \sum_{i\in \mc{I}_n}  c_{ni} \big(  I(p_i \leq  \alpha) - \P( I(p_i \leq  \alpha) \big)  \cp 0
  \end{align*}
  which follows from Lemma \ref{gwlln}. The above is equivalent to
  \begin{align*}
   \sum_{i\in \mc{I}_n}  w_i I(p_i \leq  \alpha) - \sum_{i\in \mc{I}_n} w_i  \kappa_i  \cp 0
  \end{align*}
  As $\sum_{i\in \mc{I}_n} w_i  \kappa_i\to \kappa_1$ as $n \to \infty$, by Slutsky's Theorem,
  \begin{align*}
     \sum_{i\in \mc{I}_n}  w_i I(p_i \leq  \alpha)  \cp \kappa_1,
  \end{align*}
  which finishes the proof.
\end{proof}

@@

\vspace*{0.5cm}\noindent\textbf{This needs some work (ignore for now)} Now consider a case where there exists a $2 \leq i' < n + 1$ where $\x_{1,t} = \x_{i',t}$. Now suppose for simplicity that $T^*_{j'} = T^*_1$ and that $T_{i'} = T_1$ where $T_1 > T^*_1 + q_1 + q_2 + 2$. This assumes that we have data for the first time series beyond the shock point. We will show that when there is a covariate clone of the time series under study, then estimation in this series will approximate estimation in the time series under study provided that the underlying variability is very small relative to the signal. To see this, consider $t > T^*_1$, where 
\begin{align*}
y_{1,t} &= \eta_1 + \mu_\alpha + \delta_1'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} + \sum_{j=0}^{q_2-1}(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{1} + \varepsilon_{1,t}, \\
y_{i',t} &= \eta_{i'} + \mu_\alpha + \delta_{i'}'\x_{1,T^*_1+1} + \sum_{j=1}^{q_1} (\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} + \sum_{j=0}^{q_2-1}(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} + \tilde{\varepsilon}_{i'} + \varepsilon_{i',t}, \\
\hat y_{1,t} &= \hat \eta_1 + \hat{\alpha}_1(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat y_{1,t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}, \\
\hat y_{i',t} &= \hat\eta_{i'} + \hat{\alpha}_{i'}(\x_{1,T^*_1+1}) + \sum_{j=1}^{q_1} (\hat{\phi}_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat y_{i',t-j} + \sum_{j=0}^{q_2-1}(\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}, 
\end{align*}
where $\alpha_j(\x) = \mu_\alpha + \delta_j'\x$, and we have 
\begin{align*}
  |y_{1,t} - \hat y_{1,t}| &= \Bigg\vert (\eta_1 - \hat\eta_1) + (\alpha_1 - \hat{\alpha}_1(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{1,j} + \tilde{\phi}_{1,j})y_{1,t-j} - (\hat\phi_{1,j} + \hat{\tilde{\phi}}_{1,j})\hat{y}_{1,t-j}\right] \\ 
  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{1,j+1} + \tilde{\theta}_{1,j+1})'\x_{1,t-j} - (\hat\theta_{1,j+1} + \hat{\tilde{\theta}}_{1,j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{1,t} \Bigg\vert \\
  |y_{i',t} - \hat y_{i',t}| &= \Bigg\vert (\eta_{i'} - \hat\eta_{i'}) + (\alpha_{i'} - \hat{\alpha}_{i'}(\x_{1,T^*_1+1})) + \sum_{j=1}^{q_1}\left[(\phi_{i',j} + \tilde{\phi}_{i',j})y_{i',t-j} - (\hat\phi_{i',j} + \hat{\tilde{\phi}}_{i',j})\hat{y}_{i',t-j}\right] \\ 
  &\qquad+ \sum_{j=0}^{q_2-1}\left[(\theta_{i',j+1} + \tilde{\theta}_{i',j+1})'\x_{1,t-j} - (\hat\theta_{i',j+1} + \hat{\tilde{\theta}}_{i',j+1})'\hat\x_{1,t-j}\right] + \varepsilon_{i',t} \Bigg\vert.
\end{align*}
\textbf{Needs finishing, but the argument is simple: estimation uncertainty declines as error variance decreases. And differences in the random effects decrease as variability decreases.} \vspace*{0.5cm}

\vspace*{0.5cm} We now demonstrate an idealized setting in which the above logic holds. We first present some intermediary technical results and definitions. Let $\lambda_{\text{max},\theta_k}$, $\lambda_{\text{max},\theta_\delta}$, $\lambda_{\text{max},\gamma}$ respectively be the largest eigenvalues of $\Sigma_{\theta_k}$, $\Sigma_{\delta}$, and $\Sigma_{\gamma}$ for $k = 1,\ldots,q_2$. Define  
\begin{align*}
  \mu_{\min} &= \min\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\min(\mu_\delta),\min(\mu_{\theta_k}),\min(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \mu_{\max} &= \max\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\max(\mu_\delta),\max(\mu_{\theta_k}),\max(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \lambda_{\max} &= \max\left(\lambda_{\text{max},\theta_k}, \lambda_{\text{max},\theta_\delta}, \lambda_{\text{max},\gamma}; k = 1,\ldots,q_2\right), \\
  \sigma^2_{\max} &= \max\left(\sigma^2_{\eta},\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_{\alpha},\sigma^2_{\tilde{\phi}_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right).  
\end{align*}
